### 2017-11-14 submission/manuscript.Rmd
add WIll's Intro suggestions

Our analysis found a continuous decrease in Shannon diversity from control to adenoma to carcinoma and a significantly increased relative risk for carcinoma with this lower diversity. Using only the CRC associated genera this relative risk was higher than what was observed for Shannon diversity. However, by using the full community instead of only the CRC associated genera the AUC of the classification models increased. Although we analyze a data set with a large number of total individuals each individual study was underpowered for effect size differences of 10% or below between the case and control group.

>>>>

Our analysis found a continuous decrease in Shannon diversity as disease became more severe which correlated with a significantly increased RR for carcinoma. Using only CRC-associated genera, the RR for carcinoma was higher relative to what was observed for the Shannon diversity RR. Conversely, we demonstrate that the AUC of the classification models increased when the full community was incorporated as opposed to only CRC-associated genera. Although we analyzed data sets which sampled large numbers of individuals, our results indicate the individual studies were underpowered for detecting effect size differences of 10% or below between the case and control groups.

### 2017-11-14 submission/manuscript.tex
add WIll's Intro suggestions

Our analysis found a continuous decrease in Shannon diversity from
control to adenoma to carcinoma and a significantly increased relative
risk for carcinoma with this lower diversity. Using only the CRC
associated genera this relative risk was higher than what was observed
for Shannon diversity. However, by using the full community instead of
only the CRC associated genera the AUC of the classification models
increased. Although we analyze a data set with a large number of total
individuals each individual study was underpowered for effect size
differences of 10\% or below between the case and control group.

>>>>

Our analysis found a continuous decrease in Shannon diversity as disease
became more severe which correlated with a significantly increased RR
for carcinoma. Using only CRC-associated genera, the RR for carcinoma
was higher relative to what was observed for the Shannon diversity RR.
Conversely, we demonstrate that the AUC of the classification models
increased when the full community was incorporated as opposed to only
CRC-associated genera. Although we analyzed data sets which sampled
large numbers of individuals, our results indicate the individual
studies were underpowered for detecting effect size differences of 10\%
or below between the case and control groups.
